---
title       : Growth of Orange Trees 
subtitle    : Developing Data Products Course Project using Slidify
author      : Pratheebha
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---



## About the Project

- This presentation is about the Growth of Orange Tree
- Takes a selected input for a tree and displays the circumference based on the age 
- By changing the age range using a slider changes the circumference for any selected tree.

---

## Orange Data Source 

The Orange data set contains data about the Orange trees, their age and circumference.

```{r}
library(datasets)
data(Orange)
summary(Orange)
dim(Orange)
```

---
## Code Snippet

In the below code snippet we have created some shiny widgets like an input text dropbox to select the choice of Orange tree by the tree number given, a selected tree displays the age and circumference related to that Tree.   
Also craeted a slider with ageRange as an input and takes in the paraments age as well as circumference and outputs a barplot 
displaying the change in circumference with age for a selected tree. 


inputPanel(
  selectInput("Tree", label = "Tree Number",
      choices = c(1, 2, 3, 4, 5), selected = 1),
  
  sliderInput("ageRange", label = "Age of Orange Tree:",
              min = 100, max = 1600, value = c(100, 1600),  step = 0.2)
)

---
## Sample Plot
Using the input from the slider and tree selection widget, we plot a bar plot.See below and example/plot.

```{r echo = FALSE}
library(ggplot2)
newOrange <- subset(Orange, Tree == 1)
 newOrange <- subset(newOrange, age > 100 & age < 1400) 
 
 ggplot(data = newOrange, aes(x = age, y = circumference)) + geom_bar(stat = "identity", fill = "green", color ="red") 
```  

---
Refernces
To see a full working demo of the project go to https://pratheebha-lakshminarayanan78.shinyapps.io/demo


Complete code and additional documentation can be found at  https://github.com/pratheebha/Developing-Data-Products